Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2023-01-12 response-reviewers-3.tex

\vspace{0.5cm}

% ********** comienzo del texto  *******************

{\bf Response to reviewers' comments}

We are very grateful to the editor and reviewers for their kind comments. We have rewritten
the paper quite extensively, improving grammar and, in some cases,
spelling. Additionally, we have revised references extensively, updating some
that were shown as ``under submission'' or ``accepted'', as well as fixed
capitalization in some others.

Next we will address the concerns of the single reviewer individually.

@@

\newpage

%%%% Rev 3

{\it

  {\bf Reviewer \#1}:

The paper has been significantly revised to meet the comments submitted by various reviewers. As far as I am concerned the authors have satisfactorily addressed the comments of the earlier reviewers. As is often the case, the authors have made a case to answer queries, for example, about the research questions and the significance of the study.
While addressing the queries ought to lead to accepting the submission, the issue I have is that the added text - in blue font in my copy - has significant grammatical errors. For instance, just in the first additional paragraph there are a number of issues as shown below:

New technologies are being introduced and widely adopted into the classroom in the
last years. (in recent years).

However, in order to be successful, their application will require (many)
extra work and training for the teacher, as well as for the students. (delete many).

Thus, both of them will acquire new skills and, potentially, pupils will get a higher engagement to the subject, which is usually the main objective. (pupils will be more engaged).

Therefore the new text needs a careful proofread before the submission can be accepted.}

@@

% -> answer 1

We have rewritten almost every paragraph of the paper, notably those that have
been pointed out in your review. We are again grateful for these suggestions.

### 2023-03-03 edubots_surveys.Rnw
:rotating_light:

One of the questions in the {\bf second survey}, which asked about the messaging
applications used by tertiary education teachers, opens a new line of inquiry
about what educators {\em perceive} as such, and how it is used.  Namely, the
responses indicated that teachers considered messaging applications not only
traditional chats or instant messaging apps such as WhatsApp or Microsoft Teams,
but also any means provided by their university for communicating with students,
such as a feature of the cmapus-wide learning management system that emails
grades to students. This suggests that teachers have a need for communication
with students, which is mostly unidirectional, and that it does not matter as
much how that need is met. However, this will need careful consideration,
including how it ties with the automation of the learning experience provided by
chatbots.

>>>>

One of the questions in the {\bf second survey}, which asked about the messaging
applications used by tertiary education teachers, opens a new line of inquiry
about what educators {\em perceive} as such, and how it is used.  Namely, the
responses indicated that teachers considered messaging applications not only
traditional chats or instant messaging apps such as WhatsApp or Microsoft Teams,
but also any means provided by their university for communicating with students,
such as a feature of the campus-wide learning management system that emails
grades to students. This suggests that teachers have a need for communication
with students, which is mostly unidirectional, and that it does not matter as
much how that need is met. However, this will need careful consideration,
including how it ties with the automation of the learning experience provided by
chatbots.
